---
title: "Analyse how much vCPU and RAM predict the instance limit"
author: "Raoni Smaneoto"
output:
  html_document:
    theme: readable
    df_print: paged
    toc: yes
  html_notebook:
    fig_width: 7
    theme: readable
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(boot)
library(readr)
library(here)
library(broom)
theme_set(theme_bw())
```

### The data
The data consists on a csv used by fogbow to map the user requirements to an AWS instance.
The cloud (aws) provide some instances_types that must be selected before launch it. The instances_types varies according to its attributes, like storage, vCPU, Memory, GPU etc.
```{r}
data = readr::read_csv(here::here("data/flavors.csv"))
data
```

## Data overview
```{r}
data %>% ggplot(
  aes(x=log10(Limits), y=log10(vCPU))
) + geom_line()

```

```{r}
data %>% ggplot(aes(x=log10(Limits), y=log10(Memory))) +
  geom_line()
```


## Model
```{r}
data_transformed = data %>% mutate(cpu_log=log10(vCPU), mem_log=log10(Memory), lim_log=log10(Limits)) %>%
  filter(lim_log > 0)

data_transformed %>%
  summarize(correlation_mem=cor(mem_log, lim_log, method="pearson"), correlation_cpu=cor(cpu_log, lim_log, method="pearson"))


model = lm(lim_log ~ cpu_log + mem_log, data=data_transformed)

tidy(model)
glance(model)
```

### Conclusion
I've found a expressive and negative correlation between the log10 of memory (GB) and the limits, and between log10 of cpu and limits. Besides, when I tried to find a linear model that shows how the limit changes in function of cpu_log and mem_log a expressive r_squared of 0.23 has been found.
I think it was an expressive value, because there are so many other variables that have influence in the amount of instances from a determined instance_type that can be launched. That other variables haven't been used for two reasons. The first and most important one: They don't have a pattern that could be followed when using them in the model; the second one: I was curious about how much these two variables would influence the limit.